A tutorial of Solving the defined integral problem with OpenMp

### 2023-05-28 documentation/article.tex
Url to repo added
Minor fixes

	\begin{abstract}
		The Trapezoid rule algorithm used in this tutorial is \textbf{not} the most fast method to calculate an interval defined integral but is a good example of how to make programs runs quicker by using OpenMp for parallelism. Hopefully it will help the understanding of how this library works and how to use it.
	\end{abstract}

@@

		\par The tables bellow are shows the results according to the number of threads.

>>>>

	\begin{abstract}
		The Trapezoid rule algorithm used in this tutorial is \textbf{not} the most fast method to calculate an interval defined integral but is a good example of how to make programs runs quicker by using OpenMp for parallelism. Hopefully it will help the understanding of how this library works and how to use it. All sources can be accessed at \href{https://github.com/ensismoebius/ComputacaoDeAltoDesempenho}{https://github.com/ensismoebius/ComputacaoDeAltoDesempenho}
	\end{abstract}

@@

		\par The tables bellow shows the results according to the number of threads.
